Rough Draft

### 2017-11-07 Article submission/roughdraft.tex
edited materials, methods, results, discussion

Community-driven online question and answer forums (CQA) are becoming increasingly valuable sources of information. These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. There are forums that cover a broad range of topics, like Yahoo! Answers, and forums focused on specific topics, like computer programming-focused Stack Overflow. An example of the latter is iFixit's Answers forum. As the main goal of iFixit is to enable people to fix their own devices by providing them with the knowledge and tools necessary, the Answers forum, which features questions related specifically to device repair, is a valuable source of information for this community. Thus, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

@@

    Community-driven online question and answer forums (CQA) are becoming widely used sources of information. These online platforms allow for anyone to ask or answer a question. It provides a place for people of all backgrounds and levels of expertise to provide input on a certain question. One popular CQA is Yahoo! Answers, featuring questions of all topics and expertise levels. On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers. Forums like these 2 receive around 40 million visits every month. These online question and answer forums are clearly becoming popular sources of information.

    The CQA analyzed in this paper is iFixit's Answers forum. Founded in 2003 by two engineering students at the California Polytechnic State University in San Luis Obispo, iFixit now helps thousands of people repair their broken devices everyday. The company provides over 30,000 free online repair guides with pictures and step-by-step instructions, and sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or Nexus 9 LCD digitizers. The main goal of this company is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.

    As the goal of this company is to provide people with the knowledge necessary to repair their devices, an important part of this company is their CQA, called Answers. This platform features questions related specifically to device repair, with over 9,000 device topics and over 100,000 solutions. As many rely on this forum and the community of people who provide answers, for help with their own device repairs, it's important that these users receive timely answers. Fast response times will drive up user engagement and generate more traffic, which in turn is great for the reputation and longevity of the Answers forum. As such, investigation of response times would be both beneficial and informative. Analysis can reveal factors within the forum and from elements of the questions that affect how quickly questions are answered. Suggestions for how users can ask questions to minimize answer times and for how the forum design can be improved, can be derived from such analysis.

    However, to the best of our knowledge, analysis and prediction of answer times on CQAs have not been thoroughly investigated. A majority of the existing research focuses on assessing and predicting question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's Answers forum. It attempts to determine the factors that are significantly related to answer time, and create a cox proportional hazards model that can accurately predict the failure probability of a question.

@@

    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model to analyze response times of questions posted on Stack Overflow, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.

    \citep{Mamykina2011} found that the swift answer times of Stack Overflow's community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.

    \citep{Asaduzzaman2013} analyzed unanswered questions on Stack Overflow to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.

@@

    The data analyzed in this paper contained 7,760 questions posted from April 8, 2017 to July 7, 2017, the date the data was downloaded. We worked exclusively with questions in English. Of the questions in the data set, 4,951, or 63.8\%, recieved an answer. Questions that remained unanswered were considered right-censored. The time until event variable used in survival analysis methods was defined as the time until a question posted on the forum receives an answer. Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer. We are only considering the time until the question receives its first answer. The time until answer value for right-censored questions, questions that did not receive an answer, is defined as the time from when the question was posted, to the time the data was downloaded. Figure a shows the distribution of these answer times for all questions in the data set.

    The following statistics were calculated from Kaplan-Meier estimates of questions survival probability. In this analysis, survival is defined as the event that a question remains unanswered beyond a certain time, t. As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions. For questions in this data set, the mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours. Table 1 provides more percentiles of survival time. 
    Figure A shows the Kaplan-Meier Curve for all questions in the data. The curve indicates that around 100 hours after question is posted, the probability that a question receives an answer after that time hovers around 0.35. The survival probability never reaches 0 due to the large amount of unanswered questions.

    Variables created:

    The data contained information about each question's title, text, and device, from which we created the following variables to use in the Cox regression model.

The time until a question receives its first answer was calculated as the time, in hours, from the time the question was posted to the time the first answer was received. If the question did not receive an answer, the time until answer value was calculated as the time from when the question was posted, to the time the data was downloaded, July 7, 2017 at 2:41 PM PDT. The censoring variable indicates 1 if the question received an answer, and 0 if the question remained unanswered.

@@

\begin{itemize}
  \item Device category the question pertains to. Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other. Table B shows the percentage of questions within each device category. 
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions.
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. 
  \item Whether or not the question's title ends in a question mark.
  \item Whether or not the question's title begins with a ``Wh'' word (e.g. ``What'', ``Where''). 
  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
  \item Whether or not the question's text is in all lower case. 
  \item Whether or not the asker edited or added information to the questions text sometime after posting it. 
  \item Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
  \item Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please''). (don't like the way this is worded) 
  \item Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
  \item The day of the week the question was posted. 
  \item The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night. 
\end{itemize}

@@

\begin{itemize}
  \item The average frequency, or proportion of times a tag appeared in all of the data, for all of a question's user-defined tags. Questions without tags were assigned a value of 0 for this variable. 
  \item The average number of characters in each question's tags. 
  \item The number of characters in the question's text. 
  \item The number of characters in the user-defined device name. 
  \item The ratio of the number of newlines to the number of characters in the question's text.
\end{itemize}

@@

Univariate analyses for each variable of interest were performed on one of the training data sets. Variables with a p-value of less than 0.01 were entered into the final model. As the goal of this model is prediction, it was decided that all variables would be kept in the model to maintain predictive power.

5-fold cross-validation was used to assess predictive performance. Training data sets contained 6,208 questions. Test data sets contained 1,552 questions. For each iteration, the model fit to the training data was used to calculate predicted hazard ratios from the corresponding test data. To assess prediction performance, those predicted hazard ratios were entered into a separate Cox regression model as the single predictor with the question's answer times as the survival time. The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistics for that model were used as indicators of the prediction model's performance. Significant statistics for this model would indicate that the predicted hazard ratio is signficantly associated with survival time and that our modle performs well. The concept behind these metrics came from \cite{Chen}. These metrics were also computed for predictions on the training data. For each of the five iterations, there was no signficant difference between the metrics computed on the training data prediction, and the metrics computed ont he test data. Table C shows the average metrics for training and test data predictions. The metrics evaluated were the average of all metrics computed on the test data. Although these metrics are not considerably high, they do not vary signicantly from training to test data sets.  (should I explain more about Somers' Dxy and Concordance?)

\section{Results and Discussion}

The final model included all variables described above, along with the following transformations:

\begin{itemize}
  \item Stratification on the time of day the question was posted. 
  \item Square root of the average frequency of a question's tags. 
  \item Quadratic polynomial on the length of the question's text. 
  \item Restricted cubic spline with 5 knots on the number of characters in the device name.
  \item Restricted cubic spline with 4 knots on the average number of characters in a question's tags.
  \item Restricted cubic spline with 4 knots on the ratio of newlines to the number of characters in a question's text. 
\end{itemize}

@@

The partial likelihood ratio test statistic was 1307.15 with a p-value of 0. The R-squared value for this model is 0.1555. Significant predictors with a p-value of less than 0.01 are: the Apple product, Camera, Game Console, Home, PC, and Vehicle categories of the device variable, whether or not the question's text contained at least one term considered ``frequently used'' among answered questions, whether or not question's title ended in question mark, whether or not the asker edited the question's text after posting, whether or not the asker made effort prior to posting the question to find their own solution, the average frequency of a question's tags, and average number of characters for a question's tags. Include some interpretations of the hazard ratio?

While the model is significant overall, it's predictive accuracy is low. Table blah shows metrics for the model fit to the full data set. One possible explanation for this is the high number of categorical variables included in the model. Including more quantitative variables may improve predictive accuracy. 
The data we analyzed for this model presented some limitations. Currently, askers have a considerable amount of freedom in the way they ask a question. As a result many have incorrectly specified various input fields when asking their question. For example, a question about a faulty Android tablet screen included as a tag ``someone sat on it :(''. Generally, tags are not more than a couple key words that describe the topic of the question. Many askers on this forum included lengthy and somewhat ambiguous tags in their question. Another issue was the incorrect naming of the device the asker's question was about. A user asking a question about their Turtle Beach Ear Force X device included as the name of their device "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One". The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributes to the model's low predictive accuracy.

@@

>>>>

Community-driven online question and answer forums (CQA) are becoming increasingly valuable sources of information. These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. There are forums that cover a broad range of topics, like \textit{Yahoo! Answers}, and forums focused on specific topics, like computer programming-focused \textit{Stack Overflow}. An example of the latter is iFixit's \textit{Answers} forum. The \textit{Answers} forum features questions asked by users specifically related to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices. Thus, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

@@

    Community-driven online question and answer forums (CQA) are becoming widely used sources of information. These online platforms allow for anyone to ask or answer a question, regardless of their background or expertise level. One popular CQA is Yahoo! Answers, featuring questions of all topics and expertise levels. On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers. Forums like these 2 receive around 40 million visits every month.

    The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit helps thousands of people repair their broken devices everyday. The company provides over 30,000 free online repair guides with pictures and step-by-step instructions, and sells the specialized tools and parts needed for such repairs---tools like iPhone 7 battery adhesive strips or Nexus 9 LCD digitizers. The mission of iFixit is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.

    As not all possible repairs are covered in the published repair guides, and users may have questions related to repair guides, iFixit's \textit{Answers} forum is another important resource. This platform features over 9,000 device topics and over 100,000 solutions. Questions on this forum range from broken devices like a jammed zipper to shattered iPhone screens. As many rely on this forum for help with repairs, it is important that users receive timely answers. Fast response times will enhance user engagement and generate more web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of answer times can reveal factors that affect how quickly questions are answered, which can lead to suggestions for how users can ask better questions to minimize answer times, and for how the forum design can be improved.

    However, to the best of our knowledge, analysis and prediction of answer \textit{times} on CQAs have not been thoroughly investigated. A majority of the existing research focuses on assessing and predicting question and answer quality. As such, there is need for further analysis of response times in these forums. This paper presents a survival analysis on the time until a question is answered on iFixit's \textit{Answers} forum. In order to determine factors significantly related to answer time predict the failure probability of a question.

@@

    In regards to investigation of forum response times, \citep{Bhat2014} developed a classification model to analyze response times of questions posted on \textit{Stack Overflow}, and found that tag-based features like the number of tags included or the number of subscribers a certain tag has, were the best predictors of answer time.

    \citep{Mamykina2011} found that the swift answer times of \textit{Stack Overflow's} community is a result of the reputation system and the strict emphasis on factual and informative questions and answers, rather than discussion-based.

    \citep{Asaduzzaman2013} analyzed unanswered questions on \textit{Stack Overflow} to determine common characteristics and found that questions that went unanswered shared certain characteristics in that they were too short and vague, or utilized the tagging system incorrectly.

@@

good question ex: id 408124, 406786 (answered)
bad question ex: id 410310, 405882 (unanswered)

The data analyzed contained 8,025 questions posted from April 8, 2017 (10:14 PM) to July 7, 2017 (9:28 PM) (the date the data was downloaded). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date the question was posted, date the first answer was received. Variables derived:

@@

\begin{itemize}
  \item Device category the question pertains to. Categories include: Apple Products, Android\/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, Other.
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among answered questions. See appendix for a complete list of these terms. 
  \item Whether or not the question's title contains at least one word that is considered ``frequently used'' among unanswered question. See appendix for a complete list of these terms. 
  \item Whether or not the question's title ends in a question mark.
  \item Whether or not the question's title begins with a ``Wh'' word (``Why'', ``Which'', ``When'', ``Who'', ``What'', ``Where''). 
  \item Whether or not the question's text contains any end punctuation marks (. ? !). 
  \item Whether or not the question's text is in all lower case. 
  \item Whether or not the asker edited or added information to the questions text sometime after posting it. 
  \item Whether or not the asker included a greeting (e.g. ``Hello'', ``Greetings'') in the question's text.
  \item Whether or not the asker used polite language in the question's text (e.g., ``Thank you'', ``please''). (don't like the way this is worded) 
  \item Whether or not the asker made an effort to solve the problem on their own, prior to asking the question.
  \item The day of the week the question was posted. 
  \item The time of day the question was posted. Times include: Morning, Afternoon, Evening, and Night. 
\end{itemize}

@@

\begin{itemize}
  \item The average frequency, or proportion of times a tag appeared in all of the data, for all of a question's user-defined tags. Questions without tags were assigned a value of 0 for this variable. 
  \item The average number of characters in each question's tags. 
  \item The number of characters in the question's text. 
  \item The number of characters in the user-defined device name. 
  \item The ratio of the number of line breaks to the number of characters in the question's text.
\end{itemize}

@@

    Questions analyzed were restricted to those posted in English (97\% of the full data). The time until event variable used in survival analysis is defined as the time since posting until a question receives its first answer. Comments posted on the question are not considered answers, and an answer does not have to be accepted as the ``chosen solution'' to be considered the answer. For questions that remained unanswered by the time the data was downloaded, the time until event value is defined as the time since posting to the time the data was downloaded. These questions were considered right censored, meaning that the exact answer time for these questions is unknown and greater than the recorded answer time (these questions can still receive an answer after the data was downloaded, and would then have a higher answer time than what is recorded in the data).

As there was a considerable amount of unanswered or right-censored questions, Kaplan-Meier estimates of survival probability, which adjust to the presence of these right censored observations, were assessed prior to model fitting. This method factors in the number of questions that have not been answered on each ordered time interval, based on complete answer times. The estimates of survival probablity is the product of all probabilities up to that intervals time (fix this paragraph!!!!). As such, these estimates are roughly equivalent to the conditional probability that a randomly selected question receives an answer in the next moment in time, given that it has not received an answer yet. From these estimates, curves were constructed to examine the survival experience of questions, and mean and median percentiles of survival times were calculated.

Five-fold cross-validation was used to identify potentially signficant variables and to assess model perofmrance. (explain cross-validation better, and why 5 fold was chosen) The full data was split into five training and five test data sets. Each training data set contained 6,208 questions, and each test data set contained 1,552 questions. To identify variables potentially associated with answer time, univariate analysis was performed on one of the training data sets. Each variable was entered into a Cox regression model as the single predictor with the answer time as the survival time. Variables with p-values of less than 0.01 for the likelihood ratio test were taken into consideration.

Variables identified in univariate analysis as signficant were entered into a Cox regression model. To assess predictive performance, cross-validation methods were used. For each iteration, the model was fit to one of the training data sets. The resulting model was then used to calculate predicted hazard ratios on the corresponding test data. To assess prediction performance, the predicted hazard ratios were entered into a separate Cox regression model as the single predictor with the question's answer times as the survival time. The resulting hazard ratio, R-square statistic, partial likelihood ratio and p-value, Somers' Dxy and Concordance statistics for that model were used as indicators of the prediction model's performance. Significant statistics for this model indicate that the predicted hazard ratio is signficantly associated with survival time and that our model performs well. The concept behind these metrics came from \cite{Chen}. These metrics were also computed for predictions on the training data. The metrics taken into consideration were the averages of all metrics computed on the test data.

The model with the lowest AIC statistic, and most consistent performance metrics (there wasn't significant change across iterations) was taken as the final model.

To assess the adequacy of functional forms of variables, Martingale residuals were assessed in plots.

Deviance residuals were assessed. Score residuals

Applying splines (using frank harrel's method)

To assess proportional hazards assumption, cox.zph function was used in r, assesses correlation between scaled Schoenfeld residuals and time.

\section{Results} 
(7,760 questions total), percent answered 
Figure a shows the distribution of answer times for all questions in the data set. 
summary stats from KM estimates
    The following statistics were calculated from Kaplan-Meier (explain what KM is) estimates of questions survival probability. As Kaplan-Meier estimates adjust for the presence of censored observations, these statistics are adjusted for the presence of unanswered questions. For questions analyzed, the mean survival time, or the average time until a question receives its first answer is 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer is 9.16 hours. Table 1 provides more percentiles of survival time.

        Figure A shows the Kaplan-Meier Curve for all questions in the data. The curve indicates that around 100 hours after question is posted, the probability that a question receives an answer after that time hovers around 0.35. The survival probability never reaches 0 due to the large amount of unanswered questions.

results from univariate analysis

results of metrics 
        For each of the five iterations, there was no signficant difference between the metrics computed on the training data prediction, and the metrics computed ont he test data. Table C shows the average metrics for training and test data predictions. The metrics evaluated were the average of all metrics computed on the test data. Although these metrics are not considerably high, they do not vary signicantly from training to test data sets.  (should I explain more about Somers' Dxy and Concordance?)

final model selected (with variables and transformations) 
The final model included all variables described above, along with the following transformations:

\begin{itemize}
  \item Stratification on the time of day the question was posted. 
  \item Square root of the average frequency of a question's tags. 
  \item Quadratic polynomial on the length of the question's text. 
  \item Restricted cubic spline with 5 knots on the number of characters in the device name.
  \item Restricted cubic spline with 4 knots on the average number of characters in a question's tags.
  \item Restricted cubic spline with 4 knots on the ratio of newlines to the number of characters in a question's text. 
\end{itemize}
The partial likelihood ratio test statistic was 1307.15 with a p-value of 0. The R-squared value for this model is 0.1555. Significant predictors with a p-value of less than 0.01 are: the Apple product, Camera, Game Console, Home, PC, and Vehicle categories of the device variable, whether or not the question's text contained at least one term considered ``frequently used'' among answered questions, whether or not question's title ended in question mark, whether or not the asker edited the question's text after posting, whether or not the asker made effort prior to posting the question to find their own solution, the average frequency of a question's tags, and average number of characters for a question's tags. Include some interpretations of the hazard ratio?

While the model is significant overall, it's predictive accuracy is low. Table blah shows metrics for the model fit to the full data set. One possible explanation for this is the high number of categorical variables included in the model. Including more quantitative variables may improve predictive accuracy.

assessing assumptions

@@

\section{Discussion}

The data we analyzed for this model presented some limitations. Currently, askers have a considerable amount of freedom in the way they ask a question. As a result many have incorrectly specified various input fields when asking their question. For example, a question about a faulty Android tablet screen included as a tag ``someone sat on it :(''. Generally, tags are not more than a couple key words that describe the topic of the question. Many askers on this forum included lengthy and somewhat ambiguous tags in their question. Another issue was the incorrect naming of the device the asker's question was about. A user asking a question about their Turtle Beach Ear Force X device included as the name of their device "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One". The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributes to the model's low predictive accuracy.

@@

111 terms found to be ``frequently-used'' among answered questions (ordered from highest frequency): 
screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, lcd, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top

32 terms found to be ``frequently-used'' among unanswered questions (ordered from highest frequency):
sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit
